Public's demand for moderation to online toxic speech is limited and influenced by social factors

### 2024-02-15 paper/paper2.qmd
Add files via upload

---
title: "Public's demand for moderation to online toxic speech is limited and influenced by social factors"
author: 
  - Yichen Ji
  - Xiaoxu Liu
thanks: "Code and data are available at: https://github.com/Selinayichenji/Toxic_speech_replication.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "In this report,we analysis the public's ideal moderation for 5 levels toxic online speech.It was found that most people tend to not give harsh moderations, unless the speech touches upon personal threat. And people with different social factors have difference preferences on moderations.The findings will help me build a ideal standard platform for the public."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(MetBrewer)
library(cowplot)
library(grid)
```

@@

Our paper applies using the statistical programming language R [@citeR]. Besides the programming tool, we also employ the following packages: readr [@read], broom [@broom], ggplot2 [@gg2], dplyr [@dpr], tidyverse [@tidy], MetBrewer [@met], and knitr [@citeknr].

@@

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#### Loading the Cleaned Dataset ###

lgbtq <- read_csv(here::here("data/analysis_data/lgbtq.csv"))
billion <- read_csv(here::here("data/analysis_data/billion.csv"))
partisans <- read_csv(here::here("data/analysis_data/partisans.csv"))

result_l_gender <-read_csv(here::here("data/analysis_data/lgbtq_gender.csv"))
result_l_race <-read_csv(here::here("data/analysis_data/lgbtq_race.csv"))
result_l_edu <-read_csv(here::here("data/analysis_data/lgbtq_education.csv"))

#result_b_gender <-read_csv(here::here("data/analysis_data/billion_gender.csv"))
#result_b_race <- read_csv(here::here("data/analysis_data/billion_race.csv"))
#result_b_edu <-read_csv(here::here("data/analysis_data/billion_education.csv"))

```{r, fig.width=6, fig.height=5.1}
#| echo: false
#| eval: true
#| label: fig-lgbtq-rep
#| warning: false

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity",width = 0.5) +
  theme_bw()+
  theme(
    legend.position = "bottom",
    legend.key.size = unit(0.3, "lines"),
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1)+
   guides(
    fill = guide_legend(title = "How should social media \ncompanies handle the post?",
                        title.position = "left",
                        ncol = 3,# Position the title at the top
                        byrow = TRUE)  # Arrange items by row
  ) +
  labs(x = "", y = "Percent", fill = "") +
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

@fig-lgbtq-rep illustrates the general percentages of 5 different handles in 5 levels toxic speech targets LGBTQ
. As shown on the @fig-lgbtq-rep, the serious content moderation takes more percentage as the toxic level increases. The interviewees are especially sensitive to threatening post to LGBTQ people. For no group mentioned post, most people choose to leave it, a few people put a warning. But in Threatening post, the percentages of permanently remove the post and suspend the account increase obviously, and that of other 3 decrease compared to Intolerant post, which means people choose to let those posts disappear instead other indirect moderation.

```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-gender
#| warning: false

@@

p <- ggplot(result_l_gender, aes(x = mapped_treatment, y = percentage, group = gender, color = gender)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5,  labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "Percentage by Treatment and Gender in LGBTQ Topic", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

In @fig-gender, @fig-race and @fig-educ, we visualize the difference of tendency of different groups' moderation. The plots arranges in order of the seriousness of moderation.

From @fig-gender, female tends to give more harsh moderation than male. The percentage of slightest moderation (leave it, do nothing) in male group is about 12.5% higher than that of woman in all levels toxic speech. Oppositely, the percentages of permanently remove the post and place a warning label in female group are obviously higher than male about 7%. To reduce post' view and suspend account, there is no obvious difference between 2 groups.

```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-race
#| warning: false

@@

p <- ggplot(result_l_race, aes(x = mapped_treatment, y = percentage, group = race, color = race)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5, labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "Percentage by Treatment and Race in LGBTQ Topic", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-educ
#| warning: false

@@

p <- ggplot(result_l_edu, aes(x = mapped_treatment, y = percentage, group = educ, color = educ)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5, labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "Percentage by Treatment and Education in LGBTQ Topic", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

As shown on @fig-race, white people tend to give slighter moderation than other races. Black people tend to give the harshest moderation among all races.
In @fig-educ, people with postgraduate degree tend to give slighter moderation on toxic speech. No obvious difference between College and High school graduates groups.

@@

```{r}
#| echo: false
#| eval: false
#| label: tab-appendix
#| warning: false
library(gt)

# Create a data frame with your table's content
survey_questions <- data.frame(
  Variable = c("... Support of any form of moderation", "... Political Identity", "... Social media visits", "... Age", "... Gender", "... Education", "... Race/Ethnicity", "... Attention Check", "... Emotions", "... Preference for removing the post"),
  Question = c(
    "In your view, how should social media companieslike Facebook and Twitter handle the post above?",
    "Generally speaking, do you consider yourself as being a Republican, a Democrat or an Independent?",
    "Overall, how often would you say you visit social media platforms (Twitter, Facebook, etc.)?",
    "What is your age?",
    "What is your gender?",
    "What is your highest level of educational qualification?",
    "What is your ethnicity?",
    "Please indicate your agreement with the following statement below. For our survey, it is essential that participants pay attention. To show us that you are reading this, please select both “Somewhat agree” and “Strongly agree” here.",
    "Which of the following emotions best describe your feelings about this social media post?",
    "Overall, how strongly do you feel this post should be kept or removed?"
  ),
  Response = c(
    "Leave it, do nothing (1), Place a warning label on the post (2), Reduce how many people can see the post (3), Permanently remove the post (4), Suspend the person’s account (5)",
    "Strong Democrat (1), Democrat (2), Leaning Democrat (3), Independent (4), Leaning Republican (5), Republican (6), Strong Republican (7)",
    "Every day (1) At least once a week but not every day (2), A few times a month (3), Less often (4)",
    "[Open text box]",
    "Female (1), Male (2), Other (3)",
    "Less than high school (1), High school graduate (2), Professional degree (3), College (4), Postgraduate (e.g. Masters) (5), PhD (6)",
    "White (1), Black or African American (2), American Indian or Alaska Native (3), Asian (4), Native Hawaiian or Pacific Islander (5), Hispanic (6), Other (7)",
    "Strongly disagree (1), Somewhat disagree (2), Neither agree nor disagree (3), Somewhat agree (4), Strongly agree (5) (Multiple selection is possible)",
    "Anger (Slider 0-100), Enthusiasm (Slider 0-100), Disgust (Slider 0-100), Fear (Slider 0-100), Happiness (Slider 0-100)",
    "Slider 0 (Keep the post) - 100 (Remove the post)"
  )
)

gt_table <- gt(survey_questions) %>%
  tab_header(
    title = "Table S1: Overview of survey questions and variables"
  ) %>%
  cols_label(
    Variable = "Variable",
    Question = "Question",
    Response = "Response categories"
  )
```

>>>>

---
title: "Public's demand for moderation to online toxic speech is limited and influenced by social factors"
author: 
  - Yichen Ji
  - Xiaoxu Liu
thanks: "Code and data are available at: https://github.com/Selinayichenji/Toxic_speech_replication.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "In this report,we analysis the public's ideal moderation for 5 levels toxic online speech.It was found that most people tend to not give harsh moderations, unless the speech touches upon personal threat. And people with different social factors have difference preferences on moderations.The findings will help me build a ideal standard platform for the public."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(readr)
library(knitr) 
library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(MetBrewer)
library(grid)
```

```{r load}
#| echo: false
#| warning: false
#| message: false
#### Loading the Cleaned Dataset ###

lgbtq <- read_csv(here::here("data/analysis_data/lgbtq.csv"))

result_l_gender <-read_csv(here::here("data/analysis_data/lgbtq_gender.csv"))
result_l_race <-read_csv(here::here("data/analysis_data/lgbtq_race.csv"))
result_l_edu <-read_csv(here::here("data/analysis_data/lgbtq_education.csv"))
```

@@

Our paper applies using the statistical programming language R [@citeR]. Besides the programming tool, we also employ the following packages: readr [@read], ggplot2 [@gg2], dplyr [@dpr], tidyverse [@tidy], MetBrewer [@met], knitr [@citeknr], tidyr[@tdr], kableExtra[@kbe] and grid[@grid].

@@

\newpage
## Data examples
```{r ex}
#| echo: false
#| warning: false
#| message: false

kable(head(lgbtq), "latex", booktabs = TRUE, caption = "Example of Analysis Data in LGBTQ Topic") %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```

@@

```{r, fig.width=5.5, fig.height=4}
#| echo: false
#| eval: true
#| label: fig-lgbtq-rep
#| fig-cap: Preferred actions in response to distinct post types - LGBTQ
#| warning: false

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity", width = 0.5) +
  theme_bw() +
  theme(
    plot.margin = margin(10.5, 20.5, 20.5, 5.5),
    legend.position = c(0.35, -0.17), 
    legend.key.size = unit(0.4, "lines"), 
    legend.text = element_text(size = 5), 
    legend.title = element_text(size = 7), 
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1) +
  guides(
    fill = guide_legend(
      title = "How should social media \ncompanies handle the post?",
      title.position = "left",
      ncol = 3,
      byrow = TRUE
    )
  ) +
  labs(x = "", y = "Percent", fill = "") +
  labs(title = "Target: LGBTQ") +
  theme(
    plot.title = element_text(hjust = -0.295, size = 9, face = "bold")
  )+
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

@fig-lgbtq-rep illustrates the percentages of 5 different handles in 5 levels toxic speech targets LGBTQ. As shown on the @fig-lgbtq-rep, the serious content moderations (Suspend account and Permanently remove the post) take more percentage as the toxic level increases. The interviewees are especially sensitive to threatening post to LGBTQ people. We can see that for no group mentioned post, most people choose to leave it, a few people put a warning. But in Threatening post, the percentages of permanently remove the post and suspend the account increase obviously, Interestingly, the indirect moderations'(Reduce posts' view and Put a warning label) percentages in threatening posts decrease compared to Intolerant post, but percentages direct moderations(Suspend account and Permanently remove the post) increase. This means people give up indirect method and more tend to take though and serious moderation.

In @fig-gender, @fig-race and @fig-educ, we visualize the difference of tendency of different groups' moderation. The plots arranges in order of the seriousness of moderation. Treatment is in the x-axis, ordered in posts' toxicity level, 1 to 5, from the lightest to the most toxic posts. Percentages are in y-axis. The percentage means what percent of people in specific social group takes such handle/moderation when they see the posts in x-axis. For example, the sum of all woman's percentages in Treatment 1 is 100%. If you are interested in specific numeric numbers, please check Table 3 to 5 in appendix.

```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-gender
#| fig-cap: Percentage by Treatment and Gender in LGBTQ Topic
#| warning: false

@@

p <- ggplot(result_l_gender, aes(x = mapped_treatment, y = percentage, group = gender, color = gender)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5,  labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

From @fig-gender, female tends to give more harsh moderation than male. 
Males are more inclined to take no actions than female in all toxic levels.As the toxicity of the posts increases, the tendency of females to do nothing significantly decreases, especially for threatening posts.
Both men and women are more inclined to permanently remove a post when it is threatening, but the tendency increases more sharply for women. As the toxicity of posts escalates from uncivil to threatening, both men and women are more likely to place a warning label, with women showing a slightly steeper increase in this tendency.
There is no significant gender difference for reducing posts' views, with both males and females less likely to choose this moderation for all toxicity levels of posts. Females are more likely than males to opt for suspending the account when dealing with threatening posts.
In contrast, males maintain a relatively stable tendency to moderate less than woman across all levels of post toxicity.

\newpage
```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-race
#| fig-cap: Percentage by Treatment and Race in LGBTQ Topic
#| warning: false

@@

p <- ggplot(result_l_race, aes(x = mapped_treatment, y = percentage, group = race, color = race)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5, labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

As shown on @fig-race, across all levels of post toxicity, Black individuals have the lowest tendency to take no action, especially noticeable in non-group-related (1) and control (2) posts, where their proportion of inaction rapidly decreases. Whites start with the highest proportion of inaction, which also decreases as the toxicity of the posts increases. Hispanics and Others have a moderate tendency not to act, which decreases with rising toxicity. 
When facing threatening posts (5), all racial groups show an increased tendency to remove the post, with Blacks and Hispanics showing the most significant upward trend.
As the toxicity of posts increases, all racial groups are more inclined to place warning labels on posts, with Whites and Others showing a more noticeable trend upwards.
There is little difference among racial groups in terms of reducing a post's visibility, with a general tendency not to choose this action, especially when dealing with less toxic posts.
When faced with threatening posts, the propensity to suspend accounts increases among all racial groups, with Blacks and Hispanics showing a particularly significant upward trend.
\newpage

```{r, fig.width=10, fig.height=6}
#| echo: false
#| eval: true
#| label: fig-educ
#| fig-cap: Percentage by Treatment and Education in LGBTQ Topic
#| warning: false

@@

p <- ggplot(result_l_edu, aes(x = mapped_treatment, y = percentage, group = educ, color = educ)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:5, labels = c("1", "2", "3", "4", "5")) +
  facet_wrap(~handle) +
  theme_minimal() +
  labs(title = "", x = "Treatment", y = "Percentage") +
  scale_color_brewer(palette = "Set1")

@@

As shown on @fig-educ, the inclination to take no action across all toxicity levels is relatively similar among the three education levels, with a steady decline as the posts increase in toxicity.

At toxicity levels 1 to 2, there is no significant difference among the three educational backgrounds regarding the percentage who prefer not to take any action. At toxicity levels 3 to 4, the percentage of postgraduates who choose not to take any action is noticeably higher than the other two educational backgrounds. However, when the toxicity level is at its most severe, it is the postgraduates who have the smallest proportion unwilling to take action.
Comparing the other four graphs, it can be seen that at toxicity levels 3 to 4, postgraduates have a lower percentage only in terms of putting a warning label on content. For the other three moderation actions, there is no significant difference compared to the other two educational backgrounds. However, when the toxicity level reaches the threshold of being threatening, the percentages for permanently removing the post and placing a warning label are the highest among the three educational backgrounds. Interestingly, for the most severe measure—account suspension—the percentage is actually the lowest.

In conclusion, the chart suggests that as posts become more toxic, individuals across all educational backgrounds tend to adopt stricter moderation actions. However, the variations among different educational levels are modest, with postgraduates slightly more inclined towards slighter measures (compare to suspend the account) such as putting warning label and remove the posts when dealing with the most toxic posts.

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Your data as a tibble or data.frame
survey_questions <- tibble(
  Variable = c( "Dependent Variable", "... Support of any form of moderation", "Other Variables",
                "... Political Identity", "... Social media visits", 
                "... Age", "... Gender", "... Education", "... Race/Ethnicity", 
                "... Attention Check", "... Emotions", "... Preference for removing the post"),
  Question = c("","In your view, how should social media companies like Facebook and Twitter handle the post above?","",
               "Generally speaking, do you consider yourself as being a Republican, a Democrat or an Independent?",
               "Overall, how often would you say you visit social media platforms (Twitter, Facebook, etc.)?",
               "What is your age?",
               "What is your gender?",
               "What is your highest level of educational qualification?",
               "What is your ethnicity?",
               "Please indicate your agreement with the following statement below. For our survey, it is essential that participants pay attention. To show us that you are reading this, please select both “Somewhat agree” and “Strongly agree” here.",
               "Which of the following emotions best describe your feelings about this social media post?",
               "Overall, how strongly do you feel this post should be kept or removed?"),
  Response = c("","Leave it, do nothing (1), Place a warning label on the post (2), Reduce how many people can see the post (3), Permanently remove the post (4), Suspend the person's account (5)", "",
               "Strong Democrat (1), Democrat (2), Leaning Democrat (3), Independent (4), Leaning Republican (5), Republican (6), Strong Republican (7)",
               "Every day (1) At least once a week but not every day (2), A few times a month (3), Less often (4)",
               "[Open text box]",
               "Female (1), Male (2), Other (3)",
               "Less than high school (1), High school graduate (2), Professional degree (3), College (4), Postgraduate (e.g., Masters) (5), PhD (6)",
               "White (1), Black or African American (2), American Indian or Alaska Native (3), Asian (4), Native Hawaiian or Pacific Islander (5), Hispanic (6), Other (7)",
               "Strongly disagree (1), Somewhat disagree (2), Neither agree nor disagree (3), Somewhat agree (4), Strongly agree (5) (Multiple selection is possible)",
               "Anger (Slider 0-100), Enthusiasm (Slider 0-100), Disgust (Slider 0-100), Fear (Slider 0-100), Happiness (Slider 0-100)",
               "Slider 0 (Keep the post) - 100 (Remove the post)")
)

add_blank_rows <- function(data) {
  # Create a new tibble to hold rows with blanks
  new_data <- tibble(Variable = character(), Question = character(), Response = character())

  # Add rows from original data and intersperse with blank rows
  for (i in 1:nrow(data)) {
    new_data <- add_row(new_data, data[i, ])
    # Do not add a blank row after specific rows
    if (!data$Variable[i] %in% c("Dependent Variable", "Other Variables")) {
      new_data <- add_row(new_data, Variable = "", Question = "", Response = "")
    }
  }
  return(new_data)
}

# add blank rows
expanded_questions <- add_blank_rows(survey_questions)

kable_table <- kable(expanded_questions, format = "latex", 
                     booktabs = TRUE, escape = FALSE, caption = "Overview of survey questions and variables") %>%
  kable_styling(latex_options = c("hold_position"),font_size = 8) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "6.3cm")

kable_table

```
\newpage
```{r gender_data}
#| echo: false
#| warning: false
#| message: false

result_l_gender<- result_l_gender %>%
  select(-mapped_treatment) %>%
  mutate(percentage = round(percentage, 2))

kable(result_l_gender, "latex", booktabs = TRUE, caption = "Actual Data of Gender Analysis", longtable = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

```{r race_data}
#| echo: false
#| warning: false
#| message: false

result_l_race <- result_l_race %>%
  select(-mapped_treatment) %>%
  mutate(percentage = round(percentage, 2))

kable(result_l_race, "latex", booktabs = TRUE, caption = "Actual Data of Race Analysis", longtable = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)

```{r edu_data}
#| echo: false
#| warning: false
#| message: false

result_l_edu <- result_l_edu %>%
  select(-mapped_treatment) %>%
  mutate(percentage = round(percentage, 2))

kable(result_l_edu, "latex", booktabs = TRUE, caption = "Actual Data of Education Level Analysis", longtable = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```
